Circular Regression Trees and Forests with an Application to Probabilistic Wind Direction Forecasting

### 2019-11-30 pkg/circtree/inst/wind_paper/draft/draft.Rnw
Minor stuff in draft.Rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2906 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 6b87a7f1b1391b1c967a1f2dc8478066691c1840

\Abstract{
Despite the occurrence of circular data in a wide range of scientific
fields, the existing methodology for probabilistically forecasting
circular data
is highly limited. Most of the existing methods are built on the
framework of
generalized linear and additive models, which can incorporate
difficulties in
both the optimization and the interpretation. As a very intuitive
alternative
to additive circular regression models, we extend previous ideas of circular
trees and introduce probabilistic circular regression trees and forests
employing the von Mises distribution. The resulting tree-based models
simplify
the estimation process by separating the data into more homogeneous
subgroups
and fitting a simple intercept-only model for each resulting subset. By
incorporating the framework of distributional modeling, splits in all
distribution parameters are considered and a fully specified distribution is
provided for each node.  The proposed circular regression trees are easy to
interpret, can detect non-additive effects, and select covariates and their
interactions automatically. By combining an ensemble of circular regression
trees a more stable and regularized circular regression forest can be built
which allows for modeling smooth effects as well.

@@

present a Bayesian alternative of a homoscedastic GLM for circular data.

@@

additive effects and their interpretation are not intuitive for circular responses

>>>>

\Abstract{
Despite the occurrence of circular data in a wide range of scientific
fields, the existing methodology for probabilistically forecasting
circular data
is highly limited. Most of the existing methods are built on the
framework of
generalized linear and additive models, which can incorporate
difficulties in
both the optimization and the interpretation. As a very intuitive
alternative
to additive circular regression models, we extend previous ideas of circular
trees and introduce probabilistic circular regression trees and forests
employing the von Mises distribution. The resulting tree-based models
simplify
the estimation process by separating the data into more homogeneous
subgroups
and fitting a simple intercept-only model for each resulting subset. By
incorporating the framework of distributional modeling, splits in all
distribution parameters are considered and a fully specified distribution is
provided for each terminal node.  The proposed circular regression trees are easy to
interpret, can detect non-additive effects, and select covariates and their
interactions automatically. By combining an ensemble of circular regression
trees a more stable and regularized circular regression forest can be built
which allows for modeling smooth effects as well.

@@

have presented a Bayesian alternative of a homoscedastic GLM for circular data.

@@

additive effects and their interpretation are often not intuitive for circular responses
